---
title: "Tests Knapsack using four different methods"
author: "Caspar, Nitin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tests Knapsack using four different methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The package tests Knapsack using four difference methods.

## Vignette Info

finalecasnit package tests Knapsack using Brute Force Search, Dynamic Programming, Greedy Heuristic, and Rcpp.

## Dynamic knapsack

Dynamic knapsack have been done in two version, one with loops in r, and one with loops in C++. When testing the two functions one can clearly see that the bottlenecks of is the for loops. To solve the loops are done in Rccp and a test of speed is done here under. At the writing moment there is a problem with package lineprof from Hadley Wickaham and because of this lineprof cannot be used to illustrate this the problem.
By using sys.time we can compare the two functions to see how much it improved.  

```{r}
library(finalecasnit)
set.seed(42) #Given data
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

dynamic_time<-base::system.time( knapsack_dynamic(knapsack_objects[1:8,],3500) )
print(dynamic_time)

#dynamic_Rcpp_time<- base::system.time( knapsack_dynamic_cpp(knapsack_objects[1:8,],3500))
#print(dynamic_Rcpp_time)

brute_time <-base::system.time( brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500))
print(brute_time)




```



## Brute Force Search

```{r}
library(finalecasnit)
set.seed(42) #Given data
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
## Dynamic knappsack

```{r}
knapsack_dynamic(knapsack_objects[1:8,], W = 3500)


```

## Greedy Heuristic

```{r}

greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
